Convex Surrogates via Polyhedral Losses

### 2019-02-01 cvx-fin.tex
start writing in sec 4

\raf{Got here}
It is well-known that not every property is directly elicitable.
Similarly, we will see shortly that not every elicitable property is embeddable in one dimension.
This leads to what we call embedding complexity: the minimum $d$ such that a property is $d$-embeddable.
In fact, we look at a variety of elicitation complexities restricted to various classes of losses.
In the next section, we show similarities and relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.

@@

>>>>

@@

In the previous section, we saw that every finite elicitable property is embeddable.
We now turn to a more fine-grained question: given a finite elicitable property $\gamma$, how many dimensions $d$ are required to embed $\gamma$ in $\reals^d$?
We call the minimum such $d$ the \emph{embedding dimension} of $\gamma$.

We begin with $d=1$, or real-valued embeddings.
\raf{role of orderable}
\raf{...} relationships between the elicitation complexity by various classes of loss functions, including indirect elicitation via an embedding.
